### 2015-03-02 fundamentals/impl.tex

A modular, \acrfull{ABM} approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice
to build \Cyclus on open source libraries in modern programming languages
enables both remote and multiprocess execution on a number of platforms. This
section begins by describing the general design features that make \Cyclus both
flexible and powerful: cluster-ready software and dynamic libraries.  The
\gls{ABM} framework is then described, focusing on how \gls{ABM} is implemented
in a fuel cycle context and the relative benefits thereof. A discussion of the
time-dependent treatement of discrete resources follows, focusing on the
\gls{DRE}. Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.  Lastly, the methods
for quality assurance are outlined.

@@

The architecture of \Cyclus allows developers to define nuclear fuel cycle
agents and processes independent of the simulation logic. To achieve this,
agents are developed using the \Cyclus framework \gls{API}, a set of functions
and protocols which assist in agent development and specify how agents should be
defined.  This encapsulated `plug-in' design choice provides two major
benefits. First, analysts across research institutions can take advantage of the
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
their specific problem.  A researcher can focus on creating or customizing
nuclear facility, institution, resource, and toolkit models within their
specific area of technical expertise. Second, because \Cyclus uses a modular
archetype approach, comparing two archetypes is straightforward. For example, if
an analyst would like to compare the effect of using different models to
determine the input fuel composition for fast reactors, a variety of fuel
fabrication archetypes can be developed and interchanged while keeping the rest
of the fuel cycle fixed to compare fuel fabrication designs.

@@

Groundbreaking insights and new classes of problems can be investigated by
leveraging modern massive computing resources.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures. This
severely constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed.  \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.

Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
implementation of a \Cyclus-enabled application on such a large computer system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used to run over $10^5$ jobs, comprising more than 60,000 total compute hours,
using the \Cyclus library via its resource exchange \gls{API}.  The \gls{HTC}
infrastructure has separately been utilized to run and collect information from
full \Cyclus simulations running in parallel on $10^3$ machines reliably for
order $10^5$ simulations.

@@

\Cyclus acheives this behavior by implementing its generic \gls{API} and
modular architecture via a suite of dynamically loadable plug-in libraries, as
pictured in Figure \ref{fig:framework}.
Though common in modern software architecture, such a plug-in pattern has not
previously been implemented in a nuclear fuel cycle simulator. Dynamically
loadable libraries are the primary mechanism for extending \Cyclus' capability.
This approach provides encapsulation: the core framework operates
independently from the individual plug-in libraries. Thus, any customization or
extension is implemented only in the loadable library.

@@

An additional benefit is the ability for
contributors to choose different distribution and licensing strategies
for their contributions. By allowing models to have varied
availability, the security concerns of developers can be
assuaged (See Figure \ref{fig:modifiedopen}).
In particular, since the clean plug-in architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open source archetypes without transfer of sensitive information. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

@@

This last benefit of dynamically loadable libraries addresses
another goal of \Cyclus: ubiquity amongst its potential user base. By
engineering \Cyclus to easily handle varying levels of complexity, a single
simulation engine can be used by both users interested in big-picture policy
questions as well as users focused on more detailed, technical
analyses. They merely choose their preferred level of fidelity from among the
available libraries in the ecosystem.

@@

\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated,
true to reality, and incorporates modern computing resources.
Furthermore, \gls{ABM} provides a natural
perspective from which to model a given problem. In the nuclear fuel cycle
context, for example, an analyst can design a reactor agent
that is entirely independent from a fuel fabrication agent. Defining the behavior of both agents according to the
\gls{API} contract is sufficient for them to interact with one another as
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

Furthermore, the \gls{ABM} paradigm is superior to system dynamics used in
current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model. Furthermore, because agent-based
techniques can provide a richer model than can system dynamics, they enable the
broadest range of simulations in a generic fashion.

@@

Due to this plug-in architecture,
implementations of actors in a given scenario can be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be compared to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

@@

In this way, a researcher can directly compare two different reactor modeling
implementations (perhaps \Class{DetailedReactor} and \Class{SimpleReactor})
simply by exchanging the two corresponding archetypes. That is, two reactor
archetypes both inheriting from the \Class{Facility} class are indistinguishable
from a simulation perspective. Two simulations, one using
\Class{DetailedReactor} and the other using \Class{SimpleReactor} can therefore
be compared directly to determine the whole-simulation impact of using one or the other model.
This can be done with any agent type, where agents can be ``Regions,''
``Institutions,'' or ``Facilities.''

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: production
encompassing facilities, institutions managing those facilities, and regions. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

@@

Although the \Cyclus kernel is designed around the concept of the \gls{RIF} hierarchy,
it can handle hierarchies of arbitrary depth.  It is capable of
running a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents of regions.  By
convention, institutions are mainly responsible for facility deployment, but
all archetypes have access to the agent deployment mechanism. \Cyclus enables
the developer to to implement agents that deploy copies of themselves, or that
schedule their own decommissioning.  Because regions, institutions, and
facilities are all just agents, they can all be implemented to exercise the
full set of features offered by the \Cyclus kernel.

@@

Fleet-based, lumped-material models do not distinguish between discrete facility
entities or materials. However, some questions require resolution at the level
of individual facilities and materials.  As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models. For all
of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables novel
simulations, multiple use cases require that these agents, such as the regions,
institutions, and facilities in \Cyclus, must be represented as discrete
objects. Furthermore, important use cases are enabled when materials and
resources are tracked as discrete objects alongside those agents.

@@

One such use case seeks to capture system vulnerability to nefarious
material diversion. Provenance and trade-history of distinct materials is the fundamental
information unit in such studies, and so this type of analysis requires
 discrete simulation of a
target facility and the individual materials modified within it.
Material risk analysis, therefore, demands that both facilities and materials
should be discretely modeled objects like those in \Cyclus.

In \Cyclus, agents can transfer discrete resource objects among one another.
Cyclus currently supports two types of resources:

@@

  \item Materials: These represent typical nuclear materials with
      nuclide compositions.

  \item Products: These can represent any user-defined measure - e.g. carbon
      credits, build permits, employees, etc.

@@

All operations performed on every resource object (splitting, combining,
decay, etc.) are tracked in detail as they are performed.  This information
includes the agent that created each resource when it was introduced into the
simulation.  The parentage of each resource is also tracked. This makes it
possible to follow the history of resources as they are transferred between
agents.  This powerfully impacts the ability to model
non-proliferation-related simulation goals.

@@

    \item "manual" (currently implemented) is the default mode
        where agents decay materials as needed.

    \item "never" (currently implemented) globally turns off all decay.
        The Material decay function does nothing.

    \item "lazy" (currently implemented) decays any material whenever its
        composition is observed (e.g. when an agent queries information about
        a material's $^{239}$Pu content).

    \item "periodic" (future) automatically decays all materials in a
        simulation with some fixed frequency.

@@

The \Cyclus simulation paradigm allows discrete agents, based on archetypes
about which the kernel has no knowledge, to enter the simulation at arbitrary
times and trade in discrete resources. These resources are not defined \textit{a
  priori}. Therefore, the logic engine defining resource interaction mechanisms
among agents is crucial. The \gls{DRE} is that critical logic engine on which
\Cyclus simulations are built.  Supporting the general \Cyclus philosophy,
facilities are treated as black boxes and a clear supply-demand communication
framework is defined.

@@

In \Cyclus, the \gls{DRE} is executed at each time step. Therefore, if a
facility's request for a resource is not met at a given time step, it may offer
a request in the proceeding time step. Because agent behavior may change
arbitrarily, the exchange executed at any given time step may be unique in a
simulation.

The \gls{DRE} is a novel simulation concept in the nuclear fuel cycle domain. It
provides a flexible supply-demand infrastructure, supporting dynamic flows of
resources between agents, even as those agents enter and leave the simulation, and
even when those agents are defined by archetypes of arbitrary complexity. Trading
between agents can be affected by both the
proposed quality of a resource and agent relationships through the use of
preferences. Accordingly, a wide range of possible effects can be
modeled, from capacitaty-limited fuel supply to international trade agreements.

@@

A series of utility classes are provided to support demand-constrained agent
facility deployment. For example, symbolic function representations of linear,
exponential, and piecewise functions are supported via the
\Class{SymbFunctionFactory} class. Such functions are used with other toolkit
classes to determine commodity demand (e.g., power demand) from user input. Four
mix-in classes provide the basis for in-simulation deployment determination:
\Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
interface for querying the \textit{prototypes} which have the
capacity to produce a given commdity. The \Class{CommodityProducerManager}
provides an interface for registering \Class{CommodityProducer}s and querying
the current capacity (supply) of a commodity. The \Class{Builder} class provides
an interface for querying which prototypes can be built and interacts with the
\Class{BuildingManager}, which orders prototypes to be built. The
\Class{BuildingManager} uses a simple minimum cost algorithm to determine how
many of each prototype, $y_i$, to build given a demand ($\Phi$), capacities
($\phi_i$), and costs ($c_i$).

@@

The \Cyclus toolkit provides two useful interfaces for querying physical paramaters of \Class{Material}
objects. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.

@@

In addition to those that already exist, new tools and computational patterns will
emerge from the archetypes developed within the community of
developers. As these tools gain adoption between projects and demonstrate their
utility to the developer community, they will be considered for screening and
adoption into the kernel as toolkit extensions. Likely extensions include

@@

Since \Cyclus modeling decisions are made
by third party archetype developers or users, the most important feature of
\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond
the scope of the kernel.

@@

It is important to note that before a proposed
code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all of the tests must pass.  This is a
matter of policy for the developers. Of course, test code is
just as likely to contain errors as the code it is designed to test.
However, it is assumed that diligence and one level of testing
is sufficient to meet the aims of \gls{QA} and prevent an infinite recursion
of testing-the-tests.

@@

Since these steps are performed for all incoming code, it is easyi for the
\Cyclus core team to determine whether or not an individual pull request
actually works. This helps identify build and test problems prior to
broken code being allowed into the develop branch. \gls{CI} is a necessary
but not sufficient addition to the \Cyclus \gls{QA}
system: it keeps bad code out of \Cyclus. However, \Cyclus will always
require human eyes and hands to let good code in.

>>>>

A modular, \acrfull{ABM} approach is ideal for solving the coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies which arise in \Cyclus. Additionally, the choice
to build \Cyclus on open source libraries in modern programming languages
enables both remote and multiprocess execution on a number of platforms. This
section begins by describing the general design features that make \Cyclus both
flexible and powerful: cluster-ready software and dynamic libraries.  The
\gls{ABM} framework is then described, focusing on its implementation and benefits
in a fuel cycle context. A discussion of the
time-dependent treatment of discrete resources follows, focusing on the
\gls{DRE}. Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.  Lastly, the methods
for quality assurance are outlined.

@@

The architecture of \Cyclus allows developers to define nuclear fuel cycle
agents and processes independent of the simulation logic. To achieve this,
agents are developed using the \Cyclus framework \gls{API}, a set of functions
and protocols which assist in agent development and specify how agents should be
defined.  This encapsulated `plug-in' design choice provides two major
benefits. First, analysts can take advantage of the
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
their specific problem.  A modeler can focus on creating or customizing
nuclear facility, institution, resource, and toolkit models within their
specific area of technical expertise. Second, because \Cyclus uses a modular
archetype approach, comparing two archetypes is straightforward. For example, if
an analyst would like to compare the effect of using different models to
determine the input fuel composition for fast reactors, fuel
fabrication archetypes can be developed and interchanged while keeping the rest
of the models used in the simulation fixed.

@@

Innovative approaches to designing and optimizing robust fuel cycle strategies can become available by leveraging modern parallel computing resources.  For example, large scale sensitivity analyses to quantify the dependence of fuel cycle outcomes on potentially hundreds of uncertain parameters would only be feasible in a massively parallelized environment.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures. This
constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed.  \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.

Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
implementation of a \Cyclus-enabled application on such a large computer system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. Cyclopts has run over $10^5$ jobs, comprising more than 60,000 total compute hours,
using the \Cyclus library via its resource exchange \gls{API}.  The \gls{HTC}
infrastructure has separately been utilized to run and collect information from
full \Cyclus simulations running in parallel on $10^3$ machines reliably for
order $10^5$ simulations.

@@

\Cyclus achieves this behavior by implementing its generic \gls{API} and
modular architecture via a suite of dynamically loadable plug-in libraries as
pictured in Figure \ref{fig:framework}.
Though common in modern software architecture, such a plug-in paradigm has not
previously been implemented in a nuclear fuel cycle simulator. Dynamically
loadable libraries are the primary mechanism for extending \Cyclus' capability.
The core framework operates
independently from the plug-in libraries, and the APIs are designed to provide archetype developers with the tools needed to collect inputs required by their archetype as well as return outputs. Hence the libraries enable customization and extension of \Cyclus' capabilities independent of the core.

@@

An additional benefit is the ability for
contributors to choose different distribution and licensing strategies
for their contributions. Users and modelers control the accessibility of their archetypes and data sets (See Figure \ref{fig:modifiedopen}).
In particular, since the clean plug-in architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open source archetypes without transfer of sensitive information. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

@@

Finally, dynamically loadable libraries enable \Cyclus to easily handle varying levels of simulation complexity. Hence a single
simulation engine can be used by both users interested in big-picture policy
questions as well as users focused on detailed technical
analyses. They merely choose their preferred level of modeling depth from among the
available libraries in the ecosystem.

@@

\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} provides a natural
perspective from which to model a given problem. In the nuclear fuel cycle
context, for example, an analyst can design a reactor agent
that is entirely independent from a fuel fabrication agent. Defining the behavior of both agents according to the
\gls{API} contract is sufficient for them to interact with one another as
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

Furthermore, the \gls{ABM} paradigm is superior to the system dynamic approach used in
current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model. Furthermore, because agent-based
techniques can provide a richer model than can system dynamics, they enable the
broadest range of simulations in a generic fashion.

@@

Due to this plug-in architecture,
implementations of agents in a given scenario can be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be compared to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

@@

In this way, a researcher can directly compare two different reactor modeling
implementations (perhaps the imaginary classes \Class{DetailedReactor} and \Class{SimpleReactor})
simply by exchanging the two corresponding archetypes. That is, two reactor
archetypes both inheriting from the \Class{Facility} class are indistinguishable
from a simulation perspective.  This can be done with any agent type, where agents can be ``Regions,'' ``Institutions,'' or ``Facilities.''

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

@@

Although the \Cyclus kernel is designed around the concept of the \gls{RIF} hierarchy,
it can handle hierarchies of arbitrary depth.  It is capable of
running a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents of regions. By
convention, institutions are mainly responsible for facility deployment, but
all archetypes have access to the agent deployment mechanism. \Cyclus enables
the developer to implement agents that deploy copies of themselves or
schedule their own decommissioning.  Because regions, institutions, and
facilities are all just agents, they can all be implemented to exercise the
full set of features offered by the \Cyclus kernel.

@@

Fleet-based, lumped-material models do not distinguish between discrete facility
entities or materials. However, some questions require resolution at the level
of individual facilities and materials.  As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models. For all
of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables novel
simulations, multiple use cases require that these agents, such as the regions,
institutions, and facilities in \Cyclus, must be represented as discrete
objects. For instance, tracking of individual shipments is only viable if materials and
resources are tracked as discrete objects.

@@

Another such use case seeks to capture system vulnerability to
material diversion. Provenance and trade-history of distinct materials is the fundamental
information unit in such studies, and so this type of analysis requires
 discrete simulation of a
target facility and the individual materials modified within it.
Material risk analysis, therefore, demands that both facilities and materials
should be discretely modeled objects like those in \Cyclus.

In \Cyclus, agents can transfer discrete resource objects among one another.
Cyclus supports two types of resources:

@@

  \item materials: these represent typical nuclear materials with
      nuclide compositions;

  \item products: these can represent any user-defined measure: carbon
      credits, build permits, employees, etc..

@@

All operations performed on every resource object (splitting, combining,
decay, etc.) are tracked in detail as they are performed.  This information
includes the agent that created each resource when it was introduced into the
simulation.  The parentage of each resource is also tracked. This makes it
possible to follow the history of resources as they are transferred between
agents.

@@

    \item "manual" (currently implemented) is the default mode
        where agents decay materials as needed,

    \item "never" (currently implemented) globally turns off all decay.
        The Material decay function does nothing,

    \item "lazy" (currently implemented) decays any material whenever its
        composition is observed (e.g. when an agent queries information about
        a material's $^{239}$Pu content),
    \item "periodic" (future) automatically decays all materials in a
        simulation with some fixed frequency.

@@

The \Cyclus simulation paradigm allows discrete agents, based on archetypes
about which the kernel has no knowledge, to enter the simulation at arbitrary
times and trade in discrete resources. These resources are not defined \textit{a
  priori}. Therefore, the logic engine defining resource interaction mechanisms
among agents is crucial. The \gls{DRE} is that critical logic engine on which
\Cyclus simulations are built.  Supporting the general \Cyclus philosophy,
facilities are treated as black boxes and a supply-demand communication
framework is defined.

@@

In \Cyclus, the \gls{DRE} is executed at each time step. Therefore, if a
facility's request for a resource is not met at a given time step, it may offer
a request in the following time step. Because agent behavior may change
arbitrarily, the exchange executed at any given time step may be unique in a
simulation.

The \gls{DRE} is a novel simulation concept in the nuclear fuel cycle domain. It
provides a flexible supply-demand infrastructure, supporting dynamic flows of
resources between agents, even as those agents enter and leave the simulation, and
even when those agents are defined by archetypes of arbitrary complexity. Trading
between agents can be affected by both the
proposed quality of a resource and agent relationships through the use of
preferences. Accordingly, a wide range of possible effects can be
modeled, from capacity-limited fuel supply to international trade agreements.

@@

A series of utility classes are provided to support demand-constrained agent
facility deployment. For example, symbolic function representations of linear,
exponential, and piecewise functions are supported via the
\Class{SymbFunctionFactory} class. Such functions are used with other toolkit
classes to determine commodity demand (e.g., power demand) from user input. Four
mix-in classes provide the basis for in-simulation deployment determination:
\Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
interface for querying the \textit{prototypes} which have the
capacity to produce a given commodity. The \Class{CommodityProducerManager}
provides an interface for registering \Class{CommodityProducer}s and querying
the current capacity (supply) of a commodity. The \Class{Builder} class provides
an interface for querying which prototypes can be built and interacts with the
\Class{BuildingManager}, which orders prototypes to be built. The
\Class{BuildingManager} uses a simple minimum cost algorithm to determine how
many of each prototype, $y_i$, to build given a demand ($\Phi$), capacities
($\phi_i$), and costs ($c_i$). Here $i$ indexes $I$ available prototypes which perform a similar function, and the demand, capacity and cost carry prototype-specific units which are defined by the developer.

@@

The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
objects. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.

@@

In addition to those that already exist, new tools will
emerge from the archetypes developed by the community. As these tools gain adoption between projects and demonstrate their
utility to the developer community, they will be considered for screening and
adoption into the kernel as toolkit extensions. Likely extensions include

@@

Since \Cyclus modeling decisions are made
by third party archetype developers or users, the most important feature of
\gls{QA} is verification. Validation of the \Cyclus core in a general sense is infeasible as it is contingent on the archetypes comprising a simulation, and to be meaningful \gls{UQ} must likewise extend beyond the kernel.

@@

It is important to note that before a proposed
code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.  Of course, test code is
just as likely to contain errors as the code it is designed to test.
However, it is assumed that diligence and one level of testing
is sufficient to meet the aims of \gls{QA} and prevent an infinite recursion
of testing-the-tests.

@@

Since these steps are performed for all incoming code, it is easy for the
\Cyclus core team to determine whether or not an individual pull request
actually works. This helps identify build and test problems prior to
broken code being allowed into the develop branch. \gls{CI} is a necessary
but not sufficient addition to the \Cyclus \gls{QA}
system: it keeps bad code out of \Cyclus. However, \Cyclus will always
require human eyes and hands to let good code in.
